Left-linear rewriting in adhesive categories

### 2024-04-23 concur/fusione.tex
typos

\begin{abstract}
  When can two sequential steps performed by a computing device be
  considered (causally) independent?  This is a relevant question for
  concurrent and distributed systems, since independence means that
  they could be executed in any order, and potentially in
  parallel. Equivalences identifying rewriting sequences which differ
  only for independent steps are at the core of the theory of
  concurrency of many formalisms.
  % 
  We investigate the issue in the context of the double pushout
  approach to rewriting in the general setting of adhesive categories.
  %, a very general setting for rewriting.  
  While a consolidated theory exist for so-called linear rules which
  can consume, preserve and generate entities, this paper focuses on
  left-linear rules which may also ``merge'' parts of the state.
  % 
  An apparently minimal, yet technically hard enhancement, 
  % 
  % We refine the established notion of sequential independence
  % between steps, and ...
  since % the canonical notion of independence used for linear rewriting
  % systems does not work out of the box, but it requires the
  % restriction to well-behaved classes of left-linear rules.
  % %
  % Moreover,
  a standard characterisation of independence that -- in the
  linear case -- allows one to derive a number of properties,
  essential in the development of a theory of concurrency, no longer
  holds.
  %and this requires a substantial revision of the theory.
  %
  The paper performs an in-depth study of the notion of independence
  for left-linear rules: it introduces a novel characterisation of
  independence, identifies well-behaved classes of left-linear
  rewriting systems, and provides some fundamental results including a
  Church-Rosser property and the existence of canonical equivalence
  proofs for concurrent computations. These results properly extends
  the class of formalisms that can be modelled in the adhesive
  framework.
\end{abstract}

>>>>

\begin{abstract}
  When can two sequential steps performed by a computing device be
  considered (causally) independent?  This is a relevant question for
  concurrent and distributed systems, since independence means that
  they could be executed in any order, and potentially in
  parallel. Equivalences identifying rewriting sequences which differ
  only for independent steps are at the core of the theory of
  concurrency of many formalisms.
  % 
  We investigate the issue in the context of the double pushout
  approach to rewriting in the general setting of adhesive categories.
  %, a very general setting for rewriting.  
  While a consolidated theory exists for so-called linear rules which
  can consume, preserve and generate entities, this paper focuses on
  left-linear rules which may also ``merge'' parts of the state.
  % 
  An apparently minimal, yet technically hard enhancement, 
  % 
  % We refine the established notion of sequential independence
  % between steps, and ...
  since % the canonical notion of independence used for linear rewriting
  % systems does not work out of the box, but it requires the
  % restriction to well-behaved classes of left-linear rules.
  % %
  % Moreover,
  a standard characterisation of independence that -- in the
  linear case -- allows one to derive a number of properties,
  essential in the development of a theory of concurrency, no longer
  holds.
  %and this requires a substantial revision of the theory.
  %
  The paper performs an in-depth study of the notion of independence
  for left-linear rules: it introduces a novel characterisation of
  independence, identifies well-behaved classes of left-linear
  rewriting systems, and provides some fundamental results including a
  Church-Rosser property and the existence of canonical equivalence
  proofs for concurrent computations. These results properly extends
  the class of formalisms that can be modelled in the adhesive
  framework.
\end{abstract}
